\documentclass[11pt,letterpaper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{lmodern} % clean, professional serif; works with plain pdfLaTeX, no compiler changes needed

\pagestyle{empty}
\setlength{\parindent}{0pt}

% ---- Section formatting: small caps heading, thin rule underneath ----
\titleformat{\section}{\normalsize\scshape}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{16pt}{8pt}

% ---- Tight, consistent list style for bullet points ----
\setlist[itemize]{leftmargin=14pt, itemsep=0pt, topsep=1pt, parsep=0pt}

\newcommand{\role}[4]{%
	\noindent\textbf{#1} \hfill #2\\
	\textit{#3} \hfill \textit{#4}
}

\begin{document}

% ============ HEADER ============
\begin{center}
	{\LARGE \textbf{Shruti Kamma}}\\[4pt]
	Hyderabad, India \quad $\cdot$ \quad \href{mailto:shrutikamma@gmail.com}{shrutikamma@gmail.com} \quad $\cdot$ \quad +91 93926 76095\\
	\href{https://shruti-kamma-portfolio.netlify.app}{shruti-kamma-portfolio.netlify.app} \quad $\cdot$ \quad
	\href{https://www.linkedin.com/in/shruti-kamma-71bb35312/}{linkedin.com/in/shruti-kamma} \quad $\cdot$ \quad
	\href{https://github.com/shruti-kamma}{github.com/shruti-kamma}
\end{center}

% ============ SUMMARY ============
\section*{Summary}
Product designer with full-stack development experience, seeking a design internship. Comfortable owning a problem from information architecture and user research through to a shipped, coded interface.

% ============ EDUCATION ============
\section*{Education}
\role{KL University}{Expected May 2027}{Bachelor of Technology (Honours), Computer Science and Engineering --- CGPA: 9.44}{Hyderabad, Telangana}

% ============ PROJECTS ============
\section*{Projects}

\role{CareerCraft}{March 2026}{UX/UI Designer}{}
\begin{itemize}
	\item Restructured the information architecture across 9 platform modules into one coherent learn-build-showcase-get-placed flow.
	\item Led a complete UX redesign and UI theme work in Figma --- now used by 3,000+ students across all KL University campuses.
\end{itemize}

\role{Vivaha}{June 2026 -- Present}{Product Designer \& Full-Stack Developer}{}
\begin{itemize}
	\item Designed and built the Discover matching feed for a trust-network matrimonial app --- trust-distance visualization, connector-path modal, and persisted per-profile filters.
	\item Built a shared avatar/header component system reused across 3 screens and shipped a two-tier public/private profile visibility model.
\end{itemize}

\role{Git Analyser}{July 2026 -- Present}{UI Designer \& Front-End Developer}{}
\begin{itemize}
	\item Redesigned the React frontend around GitHub's Primer design system, adding dark mode and fixing token-driven UI bugs (1,311+ lines, 30 files, open PR to main).
\end{itemize}

% ============ AUDITS (optional — you already have two real, real-product audits; worth keeping in) ============
\section*{Independent Audits}
\role{Usability \& Accessibility Audit --- CyArmorHub}{March 2026}{Informally requested by the project team}{}
\begin{itemize}
	\item Conducted a 20-finding WCAG-referenced audit across information architecture, navigation, and forms; delivered as a structured report.
\end{itemize}

\role{Usability \& Accessibility Audit --- SkaleChat}{July 2026}{Informally requested by the project team}{}
\begin{itemize}
	\item Conducted a 33-finding WCAG-referenced audit surfacing blocking onboarding bugs and Legal \& Compliance gaps; delivered as a structured report.
\end{itemize}

% ============ SKILLS ============
\section*{Skills}
\textbf{Design:} Figma, Wireframing, Prototyping, Information Architecture, Design Systems \\
\textbf{Development:} HTML, CSS, JavaScript/TypeScript, React, React Native, Astro, Git \\
\textbf{Other:} WCAG/Accessibility Auditing, Usability Testing

% ============ CERTIFICATIONS ============
\section*{Certifications}
Google UX Design Professional Certificate --- Google (Coursera), May 2026 \\
Claude Code 101 --- Anthropic, July 2026

\end{document}
